---
title: "Welcome to binomial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Welcome to binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(binomial)
```

## R Package **binomial**


The R package **binomial** implements functions for
calculating probabilities of a Binomial random variable, and related calculations such as the
probability distribution, the expected value, variance, etc.


## Calculating the probability of a binomial random variable


Use the function bin_probability().


For example, to calculate the probability of getting 2 successes in 5 trials, assuming a probability of 
success of 0.5, use:


```{r}
bin_probability(success = 2, trials = 5, prob = 0.5)
```

You might want to use this, say, to obtain the probability of getting 2 heads if you flip a fair coin 5 times.


## Obtaining the probability distribution of a binomial random variable

Use the function bin_distribution().


Suppose you want to flip a fair coin five times. he number of heads would be an example of a binomial random variable where trials = 5 and probability of success = 0.5.


The function bin_distribution will give you the probability distribution of the number of heads. That is, it will return a dataframe with the probability of obtaining each possible number of heads.


```{r}
bin_distribution(trials = 5, prob = 0.5)
```

### Obtaining the probability distribution of a binomial random variable

Use the function bin_distribution().

This will have an output similar to bin_distribution, with an added column for the cumulative probability distribution (i.e the probability that there that the number of heads is less than or equal to x)

```{r}
bin_cumulative(trials = 5, prob = 0.5)
```


